### 2011-05-04 draft2.tex
Minor fixes and prototype code.

\thispagestyle{empty}
\section{Grammars}
\subsection{$\lambda$-lifted haskell subset}
\begin{eqnarray*}
  u,e &:=& x \mid f \mid e~e \mid D \mid \bad \mid n & (Expression)\\
  p &:=& \Delta_1 \dots \Delta_n & (Program) \\
  \Delta &:=& d \mid transp (d,c) \mid opaque (d,c) & (Defintion~and~contract) \\
  d &:=& f~x_1 \dots x_n = e \mid f~x_1 \dots x_n = \mbox{ case } e \mbox{ of } [(pat_i,e_i)] & (Definition) \\
  pat &:=&D~x_1 \dots x_n & (Pattern) \\
\end{eqnarray*}

\subsection{FOL}
\begin{eqnarray*}
  t &:=& x \mid \mbox{app}(t_1,t_2) \mid k & (Term) \\
  k &:=& D \mid f \mid ? \mid \bad \mid \unr & (Constant) \\
  \phi &:=& \forall x.\phi \mid \phi \to \phi \mid \lnot \phi \mid \phi \lor \phi \mid \phi \land \phi \mid true \mid t=t \mid \mbox{CF}(t)& (Formula) \\
\end{eqnarray*}

\subsection{Contracts}
\begin{eqnarray*}
  c &:=& x:c_1 \to c_2\\
  &\mid& (c_1,c_2) \\
  &\mid& \{ x \mid e \} \\
  &\mid& \any \\
\end{eqnarray*}
We can consider CF as a user contract.

\section{Translation}
We define several translations: $\etrans{},\dtrans{},\strans{},\trans{}$.
\begin{eqnarray*}
  \etrans{} &::& Expression \to Term \\
  \dtrans{} &::& Definition \to FOF  \\
  \strans{} &::& Expression \to Contract \to FOF \\
  \trans {} &::& Definition \to Contract \to FOF \\
\end{eqnarray*}

@@

\begin{eqnarray*}
\dtrans{f~x_1 \dots x_n = e} &=& \forall x_1 \dots x_n.\etrans{f~x_1 \dots x_n} = \etrans{e} & \\
\dtrans{f~x_1 \dots x_n = \mbox{case } e \mbox{ of } [D_i~\overline{z} \mapsto e_i]} &=& \forall x_1 \dots x_n~(\bigwedge_i (\forall \overline{z}~\etrans{e} = \etrans{D_i~\overline{z}} \to \etrans{f~x_1 \dots x_n} = \etrans{e_i}) & \\
&& \land \etrans{e} = \bad \to \etrans{f~x_1 \dots x_n} = \bad)& \\ 
&& \land \trans{f~x_1 \dots x_n} = \unr \bigvee_i (\texttt{HD}(e) = D_i) & (\varphi) \\
\end{eqnarray*}

\subsection{$\strans{}$}
$\strans{e \in c}$ is a first-order formula.
\begin{eqnarray}
\strans{e \in \any} &=& true \\
\strans{e \in \{x \mid u \}} &=& \unr \lor (\mbox{CF}(\etrans{e}) \land \mbox{CF}(\etrans{u[e/x]} \neq \bad) \land \etrans{u[e/x]} \neq False) \\
\strans{e \in x:c_1 \to c_2}  &=& \forall x_1. \strans{x_1 \in c_1} \to \strans{e~x_1 \in c_2[x_1/x]} \\
\end{eqnarray}
$False$ is a data constructor here.

@@

\begin{eqnarray*}
\trans{opaque(f~x_1 \dots x_n = e,c)} &=& \dtrans{f~x_1 \dots x_n = e[f_p/f]} \land \strans{f \in c} \land \strans{f_p \in c} \\
\trans{transp(f~x_1 \dots x_n = e,c)} &=& \dtrans{f~x_1 \dots x_n = e[f_p/f]} \land \strans{f \in c} \land \strans{f_p \in c} \\
\trans{f~x_1 \dots x_n = e} &=& \trans{opaque(f~x_1\dots x_n) = e,Ok \to Ok)} \\
\end{eqnarray*}

>>>>

\thispagestyle{empty}
\section{Grammars}
\subsection{$\lambda$-lifted haskell subset}
\begin{eqnarray*}
  u,e &:=& x \mid f \mid e~e \mid D \mid \bad \mid n & (Expression)\\
  p &:=& \Delta_1 \dots \Delta_n & (Program)\\
  \Delta &:=& d \mid transp (d,c) \mid opaque (d,c) & (Defintion~and~contract)\\
  d &:=& f~x_1 \dots x_n = e \mid f~x_1 \dots x_n = \mbox{ case } e \mbox{ of } [(pat_i,e_i)] & (Definition)\\
  pat &:=&D~x_1 \dots x_n & (Pattern)\\
\end{eqnarray*}

\subsection{FOL}
\begin{eqnarray*}
  t &:=& x \mid \mbox{app}(t_1,t_2) \mid k & (Term)\\
  k &:=& D \mid f \mid ? \mid \bad \mid \unr & (Constant)\\
  \phi &:=& \forall x.\phi \mid \phi \to \phi \mid \lnot \phi \mid \phi \lor \phi \mid \phi \land \phi \mid true \mid t=t \mid \mbox{CF}(t)& (Formula)\\
\end{eqnarray*}

\subsection{Contracts}
\begin{eqnarray*}
  c &:=& x:c_1 \to c_2\\
  &\mid& (c_1,c_2) \\
  &\mid& \{ x \mid e \}\\
  &\mid& \any \\
\end{eqnarray*}
We can consider CF as a user contract.

\section{Translation}
We define several translations: $\etrans{},\dtrans{},\strans{},\trans{}$.
\begin{eqnarray*}
  \etrans{} &::& Expression \to Term\\
  \dtrans{} &::& Definition \to FOF\\
  \strans{} &::& Expression \to Contract \to FOF\\
  \trans {} &::& Definition \to Contract \to FOF\\
\end{eqnarray*}

@@

\begin{eqnarray*}
\dtrans{f~x_1 \dots x_n = e} &=& \forall x_1 \dots x_n.\etrans{f~x_1 \dots x_n} = \etrans{e} &\\
\dtrans{f~x_1 \dots x_n = \mbox{case } e \mbox{ of } [D_i~\overline{z} \mapsto e_i]} &=& \forall x_1 \dots x_n~(\bigwedge_i (\forall \overline{z}~\etrans{e} = \etrans{D_i~\overline{z}} \to \etrans{f~x_1 \dots x_n} = \etrans{e_i}) &\\
&& \land \etrans{e} = \bad \to \etrans{f~x_1 \dots x_n} = \bad)&\\ 
&& \land \etrans{f~x_1 \dots x_n} = \unr \bigvee_i (\texttt{HD}(e) = D_i) & (\varphi)\\
\end{eqnarray*}

\subsection{$\strans{}$}
$\strans{e \in c}$ is a first-order formula.
\begin{eqnarray}
\strans{e \in \any} &=& true\\
\strans{e \in \{x \mid u \}} &=& \unr \lor (\mbox{CF}(\etrans{e}) \land \etrans{u[e/x]} \neq \bad \land \etrans{u[e/x]} \neq False)\\
\strans{e \in x:c_1 \to c_2}  &=& \forall x_1. \strans{x_1 \in c_1} \to \strans{e~x_1 \in c_2[x_1/x]}\\
\end{eqnarray}
$False$ is a data constructor here.

@@

\begin{eqnarray*}
\trans{opaque(f~x_1 \dots x_n = e,c)} &=& \dtrans{f~x_1 \dots x_n = e[f_p/f]} \land \strans{f \in c} \land \strans{f_p \in c}\\
\trans{transp(f~x_1 \dots x_n = e,c)} &=& \dtrans{f~x_1 \dots x_n = e[f_p/f]} \land \strans{f \in c} \land \strans{f_p \in c}\\
\trans{f~x_1 \dots x_n = e} &=& \trans{opaque(f~x_1\dots x_n) = e,Ok \to \dots \to Ok)}\\
\end{eqnarray*}
